\documentclass[11pt, a4paper]{article}

% ---------- PACKAGES ----------
\usepackage[top=1.2cm, bottom=1.2cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{microtype}

\usepackage[normalem]{ulem}  % For underline
\setmainfont{Times New Roman}

% ---------- COLORS (for links only) ----------
\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}
\setlength{\emergencystretch}{3em}  % Avoid overfull hbox
\definecolor{sectiongray}{RGB}{60,60,60}


% ---------- SECTION STYLE ----------
\definecolor{sectiongray}{RGB}{60,60,60}

\titleformat{\section}
  {\large\bfseries\color{sectiongray}}
  {}
  {0em}
  {}
  [\vspace{2pt}\titlerule]

\titlespacing{\section}{0pt}{10pt}{6pt}



% ---------- LIST STYLE ----------
\setlist[itemize]{
    leftmargin=1.2em,
    itemsep=1.5pt,
    topsep=2pt,
    parsep=0pt
}

% ---------- DOCUMENT ----------
\begin{document}

% ================= HEADER =================
\begin{center}
{\LARGE \textbf{BRYAN STEVEN MENOSCAL SANTANA}}
\end{center}

\vspace{6pt}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l}
\textbf{Location:} Ecuador, Manabí, Manta & \textbf{Phone:} +593 99 739 9441 \\
\textbf{Email:} \href{mailto:bryanmenoscal2005@gmail.com}{bryanmenoscal2005@gmail.com}
& \textbf{Portfolio:} \href{https://stevsant.vercel.app?ref=cv-backend-en}{stevsant.vercel.app} \\
\textbf{LinkedIn:} \href{https://linkedin.com/in/bryanmenoscal26}{linkedin.com/in/bryanmenoscal26}
& \textbf{GitHub:} \href{https://github.com/StevSant}{github.com/StevSant} \\
\end{tabular*}

\vspace{6pt}
\hrule
\vspace{8pt}


% ================= SUMMARY =================
\section*{SUMMARY}

Backend Engineer focused on designing scalable, event-driven systems using Python (FastAPI, Django REST) and microservices architecture. Experience building distributed systems with Kafka, Redis, and Docker, deploying production-ready services to cloud environments. Strong emphasis on software quality through comprehensive testing strategies (unit, integration, and E2E) using PyTest.

% ================= LANGUAGES =================
\section*{LANGUAGES}
\vspace{-2pt}
\begin{tabular}{p{0.25\textwidth} p{0.7\textwidth}}
\textbf{Spanish:} & Native \\
\textbf{English:} & C1
\end{tabular}
\vspace{6pt}
\hrule
\vspace{8pt}

% ================= SKILLS =================
\section*{TECHNICAL SKILLS}
\vspace{-2pt}
\begin{tabular}{p{0.25\textwidth} p{0.7\textwidth}}
\textbf{Backend:} & Django, Django REST Framework, Flask, FastAPI, NestJS, Gin, Kafka, RabbitMQ, LangChain, LangGraph \\
\textbf{Languages:} & Python (primary), Golang, TypeScript \\
\textbf{Cloud \& DevOps:} & AWS (boto/aioboto), Google Cloud Run, Azure, Vercel \\
\textbf{Observability:} & OpenTelemetry, Prometheus, Grafana \\
\textbf{Databases:} & MySQL, PostgreSQL, MongoDB \\
\textbf{Testing:} & PyTest, Unit Testing, Integration Testing, End-to-End (E2E) Testing \\
\textbf{Tools:} & Git, Docker, Kubernetes, GitHub / GitLab, Postman, Visual Studio Code \\
\textbf{Methodologies:} & Scrum, Agile Development, DevOps, TDD \\
\end{tabular}
\vspace{6pt}
\hrule
\vspace{8pt}

% ================= EXPERIENCE =================
\section*{PROFESSIONAL EXPERIENCE}

\textbf{PATRIMORE} \hfill Remote \\
\textit{AI Agent Developer Intern} \hfill Mar 2026 -- May 2026

\begin{itemize}
\item Developed autonomous AI-assisted agents using LangGraph, FastAPI, and Anthropic SDKs (including Model Context Protocol, MCP).
\item Integrated AWS services using boto and aioboto for cloud-based workflows.
\item Implemented system observability tooling using OpenTelemetry, Prometheus, and Grafana.
\end{itemize}

\vspace{4pt}

% ================= PROJECTS =================
\section*{PROJECTS \& RELEVANT EXPERIENCE}

\textbf{SME RISK ASSESSMENT AGENT --- HACKATÓN VIAMATICA (2025)} \hfill Ecuador, Guayas, Guayaquil \\
\textit{Backend \& AI Developer | Hackathon (460+ participants, 3rd place)} \hfill 2025

\begin{itemize}
\item Built the AI agent with LangChain and the REST API with FastAPI to enable frontend communication and real-time credit risk evaluation for SMEs.
\item Implemented automated web scraping pipelines using Playwright to extract financial data from Ecuador's Superintendencia de Compañías and SRI, plus digital reputation data from Twitter, Facebook, Instagram, and LinkedIn.
\item Designed a digital reputation scoring system that incorporates SMEs' online presence into credit assessments, addressing bias in traditional evaluation methods.
\item Wrote unit and integration tests with PyTest to validate AI agent responses, scraping pipelines, and API endpoints under edge-case scenarios.
\end{itemize}

\vspace{4pt}

\textbf{STREAMFLOWMUSIC} \hfill Personal Project \\
\textit{Backend Developer} \hfill 2025

\begin{itemize}
\item Developed a scalable REST API using Django REST Framework following clean architecture principles.
\item Implemented asynchronous background tasks for media ingestion using YouTube API.
\item Optimized database queries to support 100+ concurrent users with low latency.
\item Implemented a comprehensive test suite with PyTest covering unit, integration, and E2E tests for API endpoints, background tasks, and database operations.
\end{itemize}

\vspace{4pt}

\textbf{MESAYA} \hfill Academic Project \\
\textit{Backend Developer} \hfill 2025 -- 2026

\begin{itemize}
\item Architected a microservices-based restaurant reservation platform with 7+ services using NestJS, FastAPI, Go, and Python following Clean Architecture and event-driven patterns via Apache Kafka.
\item Developed authentication (JWT), payment processing with Stripe integration, AI chatbot using LangChain/Groq, GraphQL API, and real-time WebSocket service with secure B2B webhooks (HMAC-SHA256).
\item Designed scalable PostgreSQL and Redis architecture to handle concurrent reservations and automated workflows with n8n for email notifications and third-party API integrations.
\item Built end-to-end and integration test suites with PyTest across microservices, validating inter-service communication via Kafka, payment flows, and WebSocket event handling.
\end{itemize}

% ================= EDUCATION =================
\section*{EDUCATION}

\textbf{UNIVERSIDAD LAICA ELOY ALFARO DE MANABÍ} \hfill Ecuador, Manabí, Manta \\
\textit{BSc. in Software Engineering} \hfill 2023 -- Present

\begin{itemize}
\item Development of academic and personal projects using Django REST, Flask, FastAPI, NestJS, and Angular, focused on solving real-world problems with scalable solutions.
\item Self-directed complementary training in backend, frontend, and Agile methodologies (Scrum / Kanban), reinforced through hands-on experience.
\item \textbf{Relevant coursework:} Data Structures, Software Architecture, Databases, Backend Development, Software Testing.
\end{itemize}

% ================= LEADERSHIP =================
\section*{LEADERSHIP \& VOLUNTEERING}

\textbf{Artificial Intelligence Club -- ULEAM} \hfill Ecuador, Manabí, Manta \\
\textit{Content Management Lead} \hfill 2024 -- Present

\begin{itemize}
\item Planned and structured Artificial Intelligence training curricula for the university community.
\item Supported the organization of tech talks and workshops, fostering collaborative and peer-driven learning.
\end{itemize}

\end{document}
