\documentclass[11pt, a4paper]{article}

% ---------- PACKAGES ----------
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{fontspec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}

\setmainfont{Times New Roman}

\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

% ---------- DOCUMENT ----------
\begin{document}

% ================= HEADER =================
{\large \textbf{BRYAN STEVEN MENOSCAL SANTANA}} \\
Ecuador, Manabí, Manta \\
\href{mailto:bryanmenoscal2005@gmail.com}{bryanmenoscal2005@gmail.com} \quad | \quad +593 99 739 9441 \\
\href{https://linkedin.com/in/bryanmenoscal26}{linkedin.com/in/bryanmenoscal26} \quad | \quad \href{https://github.com/StevSant}{github.com/StevSant}

\vspace{6pt}
\hrule
\vspace{12pt}

% ================= BODY =================
Dear Hiring Manager,

I enjoy solving problems --- not only large or complex ones, but any situation that creates friction, inefficiencies, or instability in a system. I find it especially satisfying to take something that isn't working well and transform it into a clear, stable, and maintainable solution.

I consider myself strong in self-directed learning and continuous improvement. I am highly proactive and constantly seeking to understand how and why systems work. In team environments, I contribute ideas, question decisions constructively when necessary, and look for ways to simplify designs while improving robustness and scalability.

As a software engineer, I'm particularly interested in software architecture and long-term system quality. I care deeply about how applications evolve over time --- scalability, clean design, performance, and maintainability are always part of how I approach development. I enjoy applying concepts such as Domain-Driven Design and event-driven systems, and I'm motivated by building resilient, well-structured applications that can grow without becoming fragile.

My goal is not just to make software work today, but to ensure it remains understandable, scalable, and reliable in the future.

\vspace{12pt}
Sincerely, \\
Bryan Menoscal

\end{document}
